Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models

### 2024-03-24 method.tex
update section 3.1 (method-framework)

\section{Our Approach}

\begin{figure*}[h]
	\centering
	\includegraphics[width=18cm]{overview.png}
	\caption{An overview of our automatic information augmentation framework. \textbf{(a) Step 1}: Interact with ChatGPT to Get Auxiliary Information. \textbf{(b) Step 2}: Distilling the Information and Injecting Them into Context \textbf{(c) Step 3}: Input the Augmented Context into Tagging Model}
	\label{fig:overview}
\end{figure*}

%\unskip
Existing extractive multi-span question answering models exhibit subpar performance in handling ambiguous words, complex proper nouns (such as film and song titles), numerical values, and long descriptive answers. The main reasons for these shortcomings can be categorized into three aspects:

\textbf{Ambiguous Words}: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context. For instance, the word ``Cameron" could refer to a famous director or a former British Prime Minister, depending on the context. The specific meanings of such words often appear infrequently in training corpora, making them difficult to learn.

\textbf{Numerical Values}: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms. For example, "22.5 billion years" can also be expressed as "cosmic years".

\textbf{Multi-span Answers}: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.

Leveraging large language models to parse question-answering data and inject auxiliary knowledge into the model can promote the integration of the model's latent world knowledge and specific domain knowledge in the paragraph, thereby enhancing the model's performance. Thus, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:

\textbf{Context Supplementary}: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts. It provides direct information prompts for low-frequency meanings or low-frequency words, achieving entity or concept alignment in the question-answering system.

\textbf{Context Enrichment}: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms. On one hand, it parses the logical relationships between other entities using entity relationship analysis. On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.

Overall,we design an automated knowledge enhancement method for multi-span question answering tasks, which interacts with large language models based on templates. This method is applicable to all question answering models or frameworks. It is universally applicable to any other downstream tasks that contain paragraph data, without the need for any complex calculations. In the following sections, we will provide a detailed introduction to each specific module of this process.

\subsection{Construction of Prompt Template}
\label{sec:prompt_construction}
\begin{figure*}[h]
	\centering
	\includegraphics[width=14.5cm]{Prompts_construction.png}
	\caption{Prompt Templates and it's Construction}
	\label{fig:prompt_template}
\end{figure*}

The quality and format of the content produced by LLMs depends greatly on the prompts. Hence, it is necessary to clarify the format and content requirements of the outputs in advance, and to refine the templates that meet the expectations through extensive evaluation.
For entity relationship parsing and textual continuation, it would be better to ensured that the the output is a natural paragraph, to facilitate the automatic splicing of the enriched knowledge with the initial paragraphs,which is consistent with encoder's natural input format.
Regarding knowledge of entity explanation, the inserted knowledge fusion method requires a parsable and structured outputs for automatic recognition and segmentation of entities and their explanations in post-processing, as well as inserting explanation behind the description of matched entity in initial context.

Concretely, by clearly specifying the form and requirements in the prompts, especially for entity relationship parsing and contextual continuation, which need to be formulated in the form of natural statements, the targeted enhanced knowledge can be obtained more easily.
Furthermore, to obtain well-structured results for complex model interactions, like entity explanations, we utilize a set of corresponding hint templates to construct the process, which has proven to be useful for interactions that require semi-structured answers through verification.

Eventually, the template is piloted to clarify any ambiguous requirements in the template to confirm an accurate understanding of the LLMs (e.g., adding at the end of the prompt, ``Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....")  In addition, to avoid omission or confusion of requirements due to the length of the prompt text, specific principles should be reiterate in a separate paragraph.

\subsection{Information Injection}

To incorporate enhanced knowledge into the original data (comprising questions and paragraphs) pertaining to entity interpretation, a methodology involving the insertion of explanations is employed. Specifically, the process begins with the automated script parsing of entity interpretation data. This script, on one hand, utilizes regular expressions to analyze the structure of the majority of sentences, while on the other hand, for a limited subset of sentences that deviate from the template specifications, employs Spacy's Semantic Dependency Analysis model to identify entities and their corresponding interpretations.

Upon obtaining the ``Entity-Entity Interpretation" knowledge base for each question-and-answer data, a subsequent scan of the original context is conducted. For each entity that exists in the dataset's library of entities and their explanations, the corresponding explanation is inserted immediately following the entity, enclosed within parentheses. This meticulous approach ensures that the augmented text, enriched with knowledge, retains its natural sentence or paragraph flow. For instance, a resulting sentence might appear as follows: ``How long does it take for the Milky Way (Milky Way: The galaxy that contains our Solar System and is home to billions of stars.) to rotate?"

@@

For the incorporation of enhanced knowledge related to entity relationship analysis and content continuation, a method of random slicing and concatenation based on length ratios is employed to infuse the augmented knowledge into the original paragraphs. Initially, the ratio of the average length of the augmented knowledge text to that of the original paragraph is calculated. Subsequently, at the model's input layer, the original input data is segmented into text fragments of length of \textit{512 * average original length / (average original length + average augmented text length)}, and the augmented text is also segmented into text fragments of length of  \textit{512 * average augmented text length / (average original length + average augmented text length)}. Then, random selections of augmented text fragments are made and concatenated into the middle of each original text fragment. Finally, this concatenated longer text is fed into the model in a sliding manner to ensure comprehensive interaction between the original data and the augmented data at lower layers of the model, as illustrated in Figure~\ref{fig:random_concatenate}.

>>>>

\section{Approach}
\subsection{our framework}
\begin{figure*}[h]
	\centering
	\includegraphics[width=18cm]{overview.png}
	\caption{An overview of our automatic information augmentation framework. \textbf{(a) Step 1}: Interact with ChatGPT to Get Auxiliary Information. \textbf{(b) Step 2}: Distilling the Information and Injecting Them into Context \textbf{(c) Step 3}: Input the Augmented Context into Tagging Model}
	\label{fig:overview}
\end{figure*}

 Given a question $Q_i \in Q = \{Q_1,...,Q_n\}$ and a context $C_i \in C = \{c_0,...,c_n\}$, where $C_i$ contains m tokens $c_0,..,c_m$, the objective of multi-span question answering is to identify a set of answer spans $A_i = \{a_0,...,a_s\}$ within the context. Here, each answer span $a_j \in A_i$ is represented as $a_j = c_{s_l},...,c_{e_l}$, where $s_l$ and $e_l$ denote the start and end positions of the l-th answer span, respectively.
 Following the observation of~\cite{li2022multispanqa}, We adopt the BIO tagging scheme to mark answer spans in the context where words are tagged as either part of the answer(\textbf{B}egin, \textbf{I}nside) or not (\textbf{O}ther). Formally, BIO tagging scheme is represented by a tag set $\tau = \{B, I, O\}$.

 Intuitively, large language models (LLMs) can serve as supplementary sources of external knowledge, compensating for the restricted semantic comprehension and limited information perception inherent in pre-trained language models). 
 We then propose a novel \textbf{G}enerative \textbf{I}nformation \textbf{A}ugme\textbf{NT}ation framework (GIANT) for multi-span question answering.
 GIANT employs a plug-and-play strategy to integrate the knowledge from large language models into the input layer of tagging models, built upon pre-trained language models.

 The overview of GIANT is depicted as \figref{fig:overview}.
 This process comprises the following steps:
 \textbf{1)Prompting}: constructing instruction templates to leverage language models for generating diversified data, involving entity elucidation, entity relationships, content continuation, and summarization.
 \textbf{2)Generating}: the large language model generating new knowledge based on the designed prompts.
 \textbf{3)Updating}: filtering the generated data, and combine it with metadata in different forms.
 \textbf{4)Training}: employing the knowledge-enhanced data to train a tagging model.

 Consider $Gen(\cdot)$ as a generative large language model, and let $Inj(\cdot)$ function as a mapping that takes the generated content $K_i$ and context $C_i$, producing the augmented context $\tilde{C_i}$. $P(\cdot)$ represents a mapping of the context $C$ onto instantiated instructions, while $Tag(\cdot)$ serves as a QA model, and $Filter(\cdot)$ denotes the sieving operation.
 With these definitions, GIANT can be formulated as follows:
 \begin{align*}
 	K_i &= Gen(C_i,P(C_i)) \tag{1}\\
 	\tilde{C_i} &= Inj(K_i,C_i) \tag{2}\\
 	A_i &= Tag(Q_i,~Filter(\tilde{C_i})) \tag{3}
 \end{align*}

 In the following section, we will explore how GIANT utilizes a large language model to generate knowledge. Subsequently, we will delve into the methods employed by GIANT to filter these knowledge, amalgamate them into meta-context, and orchestrate ensemble strategies to leverage these knowledge effectively.

\textcolor{red}{提示的模板放在哪里描述比较好？}
\label{sec:prompt_construction}
\begin{figure*}[h]
	\centering
	\includegraphics[width=14.5cm]{Prompts_construction.png}
	\caption{Prompt Templates and it's Construction}
	\label{fig:prompt_template}
\end{figure*}

\subsection{LLMs as Knowledge Source}
 GIANT employs a large language model to generate augmented data from multiple perspectives, including named entity elucidation, entity relations, content summarization, and content continuation.
 The perspectives of named entity elucidation and entity relations provide factual knowledge, with GIANT forming knowledge cues for the model by jointly injecting them into metadata. 
 Summarization acts as a mechanism for information filtering, sieving and retaining entity interpretations to ensure augmentation efficiency. 
 Content continuation introduces relevant external knowledge by extending contextual content.

\subsubsection{LLMs as Named Entity Elucidator}

  The knowledge of named entity elucidation serves as a direct aid to the model in comprehending infrequent lexical items within its pre-training corpus, context-specific terminologies in fine-tuning data, and ambiguous conceptual nuances in real world. 
  Meanwhile, the inherent robustness of large language models, owing to their sophisticated language representation capabilities and vast training corpora, facilitates the provision of more precise and comprehensive entity delineations. 
  Therefore, GIANT utilizes large language models to generate entity definitions for each question-answer pair, employing a combined approach of regular expressions and semantic dependency analysis models (Spacy) to parse the generated text and then constructs a branch-oriented "entity-elucidation" knowledge base.
  Ultimately, the obtained knowledge base is used to retrieve entity elucidations and insert them behind entities in the original context, enriching the original textual content.

@@
